MR-PFU: A suite of R packages for energy conversion chain analysis

### 2023-07-21 paper.Rmd
Updated statement of need.

Historically, SEA has analyzed energy flows through specific countries
using Excel spreadsheets, 
with data in varying and inconsistent formats 
[@Ayres:2003ec; @Serrenho:2014aa; @Brockway:2014aa; @Brockway:2015aa].

>>>>

Historically, SEA has analyzed energy flows through specific countries
using spreadsheets, 
with data in varying and inconsistent formats 
[@Ayres:2003ec; @Serrenho:2014aa; @Brockway:2014aa; @Brockway:2015aa].
Scientists in the field wanted to expand to cover all countries, but
the spreadsheet approach to data analysis would not scale.
We developed a series of `R` packages to enable 
analyses for all countries, as described in the following table.
